---
name: Martin
surname: Čadek
position: ""
address: ""
phone: +44 07715 208 734
www: martincadek.com
email: "cadekmail@gmail.com"
twitter: m_cadek
github: ""
linkedin: martincadek
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 005999
aboutme: "I am on the journey towards a career in data science, analytics, and statistics. I am looking for the best place to apply my knowledge from my degree in psychology and doctorate that focused on health communication, public health, and behaviour science. I enjoy the process of scientific inquiry and solving challenging problems. I am constantly learning and thrive in a challenging but supportive environment."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae) # https://pkg.mitchelloharawild.com/vitae/
library(tibble)
library(dplyr)
library(tinytex)
library(glue)
library(here)
source(file = here("data/experience.R")) # R file with experiences section
source(file = here("data/courses.R")) # R file with courses section
source(file = here("data/community.R")) # R file with community section
source(file = here("data/education.R")) # R file with education section
# https://github.com/tallguyjenks/CV (inspired by)
# http://chrisumphlett.com/posts/vitae-package/ (inspired by)
```

# Skills

## Data Science

-   Exploratory data analysis, machine learning and regression analysis {caret, tidymodels, car, lme4}, data wrangling {tidyverse, data.table}, dashboard development {shiny}, data visualization {ggplot2, plotly}, classification {tidymodels}, computerised text mining {quanteda, tidytext}, continuous deployment {netlify}, reproducibility {rmarkdown, renv, virtual environments}

## Applications

-   RStudio, Visual Studio Code, SPSS, Tableau, Excel, Qualtrics

## Languages

-   R {ggplot2, Shiny, data.table, tidyverse, tidymodels, quanteda, tidytext, caret, car}, SQL {Postgre}, Git {GitHub, GitLab}, Python {pandas}, RMarkdown, latex, CSS

# Experience

```{r experience}
# The .protect = FALSE allows latex to be implemented;
# Not used in other parts
experience %>% 
     detailed_entries(role, dates, company, location, details, .protect = FALSE)
```

# Courses

```{r courses}
courses %>% 
  detailed_entries(organisation, dates, category, location, description)
```

# Community

```{r community}
community %>%
  detailed_entries(role, dates, activity, location, details)
```

# Education

```{r education}
education %>% 
  detailed_entries(degree, dates, uni, loc) # , details
```
