---
name: Martin
surname: Čadek
position: "Data Scientist"
address: ""
www: www.martincadek.com
email: "cadekmail@gmail.com"
github: ""
linkedin: martincadek
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
aboutme: "Data scientist passionate about healthcare, and former researcher with doctorate degree (PhD) in psychology which focused on health communication, public health, and obesity interventions. User of data analytics software and programming languages suitable for providing analytical and statistical solutions such as R, Python, and SAS. Advocate of reproducible research with the use of version control (git, docker, makefiles), reproducible reports (shiny, markdown)."
output: 
     vitae::awesomecv:
          page_total: true
---


```{r setup_vitae, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
library(vitae) 
# https://pkg.mitchelloharawild.com/vitae/
# https://github.com/tallguyjenks/CV (inspired by)
# http://chrisumphlett.com/posts/vitae-package/ (inspired by)
# Additional R Packages:
library(tibble)
library(dplyr)
library(tinytex)
library(glue)
library(here)
```


```{r setup_others, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source(file = here("data/experience.R")) # R file with experiences section
source(file = here("data/courses.R")) # R file with courses section
source(file = here("data/community.R")) # R file with community section
source(file = here("data/education.R")) # R file with education section
```

# Skills

## Data Science

-   Exploratory data analysis, machine learning and regression analysis {tidymodels, car, lme4}, data wrangling {tidyverse, data.table}, dashboard development {shiny}, data visualization {ggplot2, plotly}, computerised text mining {quanteda, tidytext}, continuous deployment {netlify}, reproducibility {rmarkdown, renv, venv, miniconda}

## Applications

-   RStudio, VS Code, SAS, Tableau, Excel, Qualtrics

## Languages

- R {ggplot2, Shiny, data.table, tidyverse, tidymodels, quanteda, tidytext}
- Python {pandas, scikit-learn}
- SQL {Postgre}
- Git {GitHub, GitLab}
- SAS

# Experience

```{r experience}
# The .protect = FALSE allows latex to be implemented;
# Not used in other parts
experience %>% 
     detailed_entries(role, dates, company, location, details, .protect = FALSE)
```

# Courses

```{r courses}
courses %>% 
  detailed_entries(organisation, dates, category, location, description)
```

# Community

```{r community}
community %>%
  detailed_entries(role, dates, activity, location, details)
```

# Education

```{r education}
education %>% 
  detailed_entries(degree, dates, uni, loc) # , details
```
